\documentclass{ieeeaccess}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{url}
\usepackage{arydshln}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2026.DOI}

\title{Measuring the Emotion--Speaker Tradeoff Frontier in Emotional Voice Conversion}

\author{\uppercase{Bashar M.Deeb}\authorrefmark{1}}
\address[1]{Department, University, City, Country (e-mail: author@example.com)}
\corresp{Corresponding author: Bashar N. Placeholder (e-mail: author@example.com).}

\begin{abstract}
Emotional voice conversion aims to modify the perceived emotion of speech while preserving linguistic content and speaker identity.
This paper studies emotional conversion as an intensity-conditioned frontier between target-emotion strength and speaker preservation.
We distinguish inferred intensity sweeps, which traverse an existing style representation after training, from native intensity sweeps, which use a learned intensity-control mechanism inside a StarGANv2-VC-based architecture.
We evaluate the resulting frontier on ESD and CREMA-D from-scratch settings using emotion-side metrics, speaker-side metrics, speaker-related ablations, model-comparison significance tests, and a listening study where available.
Across ESD conditions, stronger emotion control improves emotion-side metrics while reducing source-speaker similarity, and the ESD single-speaker listening study shows the same perceptual direction.
CREMA-D from-scratch results behave as a harder stress test rather than as a clean replication of ESD.
Speaker-related ablations show that additional speaker supervision is not automatically beneficial: it can shift the operating curve, improve some speaker-side metrics, and still reduce continuous emotion-similarity metrics.
The results support reporting emotional voice conversion as a frontier over intensity rather than as independent aggregate emotion and speaker scores.
\end{abstract}

\begin{keywords}
Emotional voice conversion, emotion intensity, speaker identity, speaker similarity, voice conversion, evaluation.
\end{keywords}

\titlepgskip=-15pt

\maketitle

\input{sections/01-introduction}
\input{sections/02-related-work}
\input{sections/03-method}
\input{sections/04-results}
\input{sections/05-discussion}
\input{sections/06-conclusion}

\section*{Acknowledgment}
The authors thank the participants in the listening study.

\bibliographystyle{IEEEtran}
\bibliography{../../sources}

\begin{IEEEbiography}{Bashar N. Placeholder}
Biography text will be added before submission.
\end{IEEEbiography}

\EOD

\end{document}
